The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-13 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

First, we see a statistically significant change
in home win percentage in 2020 from 2017-19, with p-value of 0.0365 for the
z-test and 0.0400 for Fisher's test. The 95% confidence interval of (-0.255, -0.008) 
confirms our belief that home-court advantage was lost in the 2020 NBA playoffs. However, after accounting for
multiple tests using the Bonferroni correction, the p-values for both tests are no longer significant.
So, we may only cautiously say there is evidence that home-court advantage was
not a factor in 2020.

>>>>

First, we see a statistically significant change
in home win percentage in 2020 from 2017-19, with p-value of 0.0497 for the
z-test and 0.0400 for Fisher's test. The 95% confidence interval of (-0.255, -0.008) 
confirms our belief that home-court advantage was lost in the 2020 NBA playoffs. However, after accounting for
multiple tests using the Bonferroni correction, the p-values for both tests are no longer significant.
So, we may only cautiously say there is evidence that home-court advantage was
not a factor in 2020.
